Summary Tables

### 2020-02-13 summary_tables_outcomes.Rmd
Fix minor mistake
Add table for injury per 100k

### No Other Vehicle matrix matrix for baseline {#nov_baseline}

@@

>>>>

### No Other Vehicle matrix for baseline {#nov_baseline}

@@

### Change in inury per 100K

```{r inj_100k = "asis"}
require(tibble)

for (city in cities){

  print(city)

  el <- list()

  if (!city %in% c('buenos_aires', 'mexico_city', 'bogota', 'vizag')){

    for (cs in names(io[[city]]$outcomes$whw)){
      #cs <- 'Baseline'
      #city <- 'accra'
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      td4 <- io[[city]]$dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode, cs)

      if (length(el) == 0){
        el <- td4 %>% dplyr::select(stage_mode)
      }

      td4 <- left_join(td4, td3 %>% dplyr::select(mode, count) %>% rename(stage_mode = mode), by = 'stage_mode')

      td5 <- td4

      td4[, 2] <- round((td4[,3] / td4[,2]) * 100000, 1)

      names(td4)[3] <- paste(names(td4)[2], names(td4)[3], sep = "_")

      el <- inner_join(el, td4, by = 'stage_mode')

      # for (i in 1:nrow(td4)){
      #   td4[i, 2:(ncol(td4) - 2)] <- round((td4$total[i] /(td4[i, 2:6])) * 100000, 1)
      #   
      #   
      # }

      # print(td4)
    }
    print(kable(el, caption = city))
    cat("\n")
    #kable(print(el), caption = city)
  }

}
```
